Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-03 paper-ieee-trans.tex

\begin{IEEEbiography}\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/cris_foto_good}}]{Doina Cristina Duma}
is the leader of the Distributed Systems group at the INFN National Center (CNAF), providing the core operational support for the INFN-wide Grid infrastructure and for the CNAF Cloud infrastructure. She has a long experience in managing distributed e-infrastructures, being involved since 2003 in major European projects such as DataGrid, EGEE (I, II, III), EGI-Inspire and EGI-Engage. She was the Release Manager of the EMI (European Middleware Initiative) and INDIGO - DataCloud European project project and having as main responsibilities to manage all release activities, including release planning, building, deploying, reporting, establishing and maintaining the overall release timeline and milestones.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/cris_foto_good}}]{Doina Cristina Duma}
is the leader of the Distributed Systems group at the INFN National Center (CNAF), providing the core operational support for the INFN-wide Grid infrastructure and for the CNAF Cloud infrastructure. She has a long experience in managing distributed e-infrastructures, being involved since 2003 in major European projects such as DataGrid, EGEE (I, II, III), EGI-Inspire and EGI-Engage. She was the Release Manager of the EMI (European Middleware Initiative) and INDIGO - DataCloud European project project and having as main responsibilities to manage all release activities, including release planning, building, deploying, reporting, establishing and maintaining the overall release timeline and milestones.
\end{IEEEbiography}
